% 
\documentclass[10pt]{article}



\usepackage{url}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{xcolor}
% \usepackage{fancyhdr}

\geometry{verbose,paperwidth=21cm,paperheight=29.7cm}
\geometry{tmargin=20mm,bmargin=25mm,lmargin=20mm,rmargin=20mm}

% \fancyhead{}
% \fancyhead[LO]{Team Mask (Group 09): Rahul Rao, Rajath Acharya, Ramu Ramasamy, Sachin Sudhakar Shetty, Vishwas}
% \fancyfoot[LO]{Interactive Data Visualization}
% \fancyfoot[E]{\thepage}
% \fancyfoot[R]{\thepage}
% \fancyfoot[C]{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% configure these settings and you are good to go %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\participant}{Team Mask (Group 09)}
\newcommand{\affiliation}{Paderborn University}
% \urldef{\emailaddress}\url{<my-UPB-email-address>}
\newcommand{\topic}{Assignment 5: Group Project Interactivity}
\newcommand{\submissiondate}{June 17, 2020}

% 

\begin{document}

\title{\topic}
\author{\Large{\participant}\\ \affiliation \\}
\date{\submissiondate}
\maketitle
\thispagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% here starts the actual text                     %%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}
%\label{sec:introduction}

\color{black}
At present, where University, Organization, Institution, Restaurant and many more are entirely shut or made online except Hospitals which are working 24*7, yes its {\bf COVID-19}. A pandemic which has shaken the economy of the world. As the battle continues, data sets corresponding to the virus disease are collected around the globe. This concept paper is on the Topic: COVID-19 as part of the Assignment to the subject Module: Interactive Data Visualization which we here summarize about the dataset of COVID-19 disease used, visualizations, and interaction end-user can probably expect.

\section{Data Characteristics}

The dataset characteristics are described in the Table \ref{tab:data_chars}. The dataset \textit{owid-covid-data.csv} is comprised of the dataset sources listed in the Table \ref{tab:data_sources} and is available as comma separated strings. The dataset contains 22,873 records and 33 columns (on June 12, 2020). Also, dataset containing the polygons, used to form a World Map for representing geo spatial mapping information is sourced from Natural Earth (Admin-0 Countries). 

% that include European Centre for Disease Prevention and Control, National government reports, United Nations, Department of Economic and Social Affairs, Population Division, World Population Prospects: The 2019 Revision, World Bank – World Development Indicators, sourced from Food and Agriculture Organization and World Bank estimates, UN Population Division, World Population Prospects, 2017 Revision, United Nations Statistics Division, and OECD, Eurostat, World Bank, national government records and other sources.

\begin{table}[htbp]
    \centering
    \begin{tabular}{|p{6cm}|p{6cm}|}
        \hline
        European Centre for Disease Prevention and Control &  National government reports \\
        \hline 
        Department of Economic and Social Affairs & United Nations \\
        \hline
        World Population Prospects: The 2019 Revision & Population Division \\
        \hline 
        OECD & Eurostat \\
        \hline
        World Bank – World Development Indicators, sourced from Food and Agriculture Organization and World Bank estimates &  UN Population Division, World Population Prospects, 2017 Revision\\
        \hline
    \end{tabular}
	\caption{Sources}
	\label{tab:data_sources}
\end{table}




\section{User and Task}
The owid-covid-19-data dataset captures information of disease spread and fatalities caused around the globe and also counter measure like testing taken by respective countries.\newline
Tasks for the Visualization can be as follows:
\begin{itemize}
    \item Visualization of disease information country-wise taking into account of multivariate data like infected cases, fatality count, total cases and total deaths per million.
    \item Visualization by comparison of the total cases and fatalities by nations monthly.
    \item Visualization of increasing or decreasing trends of total cases/total deaths of the selected nations.
    \item Visualization of total cases/fatalities per million for each country.
\end{itemize}
Probable target users:
\begin{itemize}
    \item The general public can get to know the statistics of COVID-19 over the globe. 
    \item WHO and independent government bodies of countries can make use of the visualizations for better planning of the medical infrastructure. 
    \item Monetary Institution like World Bank can estimate the impact of the losses particular to a region and aid respectively.
    \item Travel and Tourism industry and service providing organization can utilize these visualizations for better trip planning.
\end{itemize}


\section{Visualization Technique}
Visualization by multiple visulization technique interconnected by user interaction. Geospatial visualization will act as the root of the other visulization techniques. 
\begin{itemize}
    \item \textbf{Geospatial Visualization:} A choropleth world map that differentiates cases-reported/fatalities/case-per-million/deaths-per-million using brightness as a visual variable based on locations and their associated data values.
    \item \textbf{Time Visualization:} A bar-chart which compares the cases-reported/fatalities/case-per-million/deaths-per-million with respect to time-oriented data(monthly) along x-axes, for the selected country in the choropleth map. 
     \item \textbf{Line Graph Visualization:} A line plot displaying univariate data, showing the increase or decreasing trend for the selected country and associated univariate data.
\end{itemize}


\section{Interaction}
\begin{itemize}
    \item \textbf{Interaction Operands - Screen Space:} On hovering on the choropleth map particular region of the country,
    multivariate data values such as the total number of cases and the total number of deaths can be displayed as a tooltip from the screen.
    \item \textbf{Interaction Operators - Connection Operators:} On-click event on the region (country) in the choropleth map,
    corresponding data values are mapped to the bar chart representation of similar data which shows the different perspectives of the COVID-19 related information.
    \item \textbf{Interaction Operators - Selection:} A drop-down menu will be provided to the user, and legend to 
    where the user can select from the drop-down list and view geospatial representation of COVID-19 related information by varying the intensity of color in the choropleth world map
\end{itemize}
%\label{sec:First_Section}

\begin{table}[htbp]
    \centering
	\begin{tabular}{|l|l|p{8cm}|}
		\hline
		\textbf{Data} & \textbf{Data Type} & \textbf{Description} \\
        \hline \hline
        iso\_code & String & ISO 3166-1 alpha-3 (3 letter country codes) \\
        \hline
        continent & String & Continent name \\
        \hline
        location & String & Country name \\
        \hline
        date & String & Date of observation \\
        \hline
        total\_cases & int64 & Total confirmed cases of COVID-19 \\
        \hline
        new\_cases & int64 & New confirmed cases  \\
        \hline
        total\_deaths & int64 & Total deaths attributed \\
        \hline
        new\_deaths & int64 & New deaths \\
        \hline
        total\_cases\_per\_million & float64 & Total confirmed cases per one million people \\
        \hline
        new\_cases\_per\_million & float64 & New confirmed cases per one million people  \\
        \hline
        total\_deaths\_per\_million & float64 & Total deaths per one million people \\
        \hline
        new\_deaths\_per\_million & float64 & New deaths per one million people \\
        \hline
        total\_tests & float64 & Total tests conducted \\
        \hline
        new\_tests & float64 & New tests conducted \\
        \hline
        new\_tests\_smoothed & float64 & New tests (7 day smoothed). For countries not reporting data on daily basis. \\
        \hline
        new\_tests\_per\_thousand & float64 & New tests per thousand people \\
        \hline
        new\_tests\_smoothed\_per\_thousand & float64 & New tests per thousand people (7 day smoothed) \\
        \hline
        tests\_units & float64 & Units used by the location to report the testing data \\
        \hline
        population & float64 & Population in 2020 \\
        \hline
        population\_density & float64 & Number of people divided by land area, measured in square kilometers, most recent year available. \\
        \hline
        median\_age & float64 & Median age of the population, UN projection for 2020. \\
        \hline
        aged\_65\_older & float64 & Share of the population that is 65 years and older. \\
        \hline
        aged\_70\_older & float64 & Share of the population that is 70 years and older in 2015. \\
        \hline
        gdp\_per\_capita & float64 & Gross domestic product at purchasing power parity (constant 2011 international dollars), most recent year available. \\
        \hline
        extreme\_poverty & float64 & Share of the population living in extreme poverty, most recent year available since 2010. \\
        \hline
        cvd\_death\_rate & float64 & Death rate from cardiovascular disease in 2017. \\
        \hline
        diabetes\_prevalence & float64 & Diabetes prevalence (\% of population aged 20 to 79) in 2017. \\
        \hline
        female\_smokers & float64 & Share of women who smoke, most recent year available. \\
        \hline
        male\_smokers & float64 & Share of men who smoke, most recent year available. \\
        \hline
        handwashing\_facilities & float64 & Share of the population with basic handwashing facilities on premises, most recent year available. \\
        \hline
        hospital\_beds\_per\_thousand & float64 & Hospital beds per 1,000 people, most recent year available since 2010. \\
        \hline
    \end{tabular}
	\caption{Data Characteristics}
	\label{tab:data_chars}
\end{table}




%% the following commands include the biliographic information (in BibTeX format) from the 
%% file template.bib
%\bibliography{Template_One_Pager.bib}
%\bibliographystyle{plain}

\end{document}
